\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2017-01-06 Response.tex

\documentclass[11pt]{article}
\usepackage[letterpaper,margin=1in,centering]{geometry}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amssymb}  
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{siunitx}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{color}
\usepackage{bm}
\usepackage{xr-hyper}
\usepackage{hyperref}
\usepackage[]{cleveref} % get fancy referencing

\externaldocument[]{manuscript}[manuscript.pdf]

% edit cref citations for IEEE format
\crefformat{equation}{(#2#1#3)} % no abbreviation for equation numbers
\Crefformat{equation}{Equation~(#2#1#3)} % no abbreviation for equation numbers
\crefrangeformat{equation}{(#3#1#4--#5#2#6)}
\Crefrangeformat{equation}{(#3#1#4--#5#2#6)}
\crefmultiformat{equation}{(#2#1#3)}{ and~(#2#1#3)}{, (#2#1#3)}{ and~(#2#1#3)}
% edit cref citations for IEEE format
\crefformat{figure}{Fig.~#2#1#3} % no abbreviation for equation numbers
\Crefformat{figure}{Fig.~#2#1#3} % no abbreviation for equation numbers
\crefrangeformat{figure}{Figs.~#3#1#4--#5#2#6}
\Crefrangeformat{figure}{Figs.~#3#1#4--#5#2#6}
\crefmultiformat{figure}{Figs.~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
% for items in a list
\crefformat{enumi}{(#2#1#3)}
\Crefformat{enumi}{Item~(#2#1#3)} 
\crefrangeformat{enumi}{(#3#1#4--#5#2#6)}
\Crefrangeformat{enumi}{Items~(#3#1#4--#5#2#6)}
\crefmultiformat{enumi}{(#2#1#3)}{ and~(#2#1#3)}{, (#2#1#3)}{ and~(#2#1#3)}
% Proposition format
\crefformat{prop}{Proposition~#2#1#3} % no abbreviation for equation numbers
\Crefformat{prop}{Proposition~#2#1#3} % no abbreviation for equation numbers
\crefrangeformat{prop}{Proposition~#3#1#4--#5#2#6}
\Crefrangeformat{prop}{Propositions~#3#1#4--#5#2#6}
\crefmultiformat{prop}{Propositions~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
% Appendix
\crefformat{appendix}{Appendix~#2#1#3} % no abbreviation for equation numbers
\Crefformat{appendix}{Appendix~#2#1#3} % no abbreviation for equation numbers
\crefrangeformat{appendix}{Appendices~#3#1#4--#5#2#6}
\Crefrangeformat{appendix}{Appendices~#3#1#4--#5#2#6}
\crefmultiformat{appendix}{Appendices~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}

@@

\end{correction}

In addition,~\Cref{prop:config_error} was modified to include additional detail on the notation \( \dirDiff{f}{x}\) as
\begin{correction}
    The variation of \( B(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
    \begin{align*}
        \dirDiff{B}{R} &= \eta \cdot e_{R_{B}} ,
    \end{align*}
  where the notation \( \D_R A \) and \(\D_R B\) represents the derivative of \( A \) or \( B \) with respect to \( R\).
\end{correction}

\item \textit{This is serious. In section 2, the upper bounds listed in Proposition 4 are given. Well, these should be the properties that your controller guarantees not come from the set D you've defined. Since these properties are used to derive the bound H which is used to derive the result in Proposition 5, the stability proof under the proposed controller is far from complete.}

The stability proof has been improved and several modifications have been included in the manuscript:
\begin{itemize}
    \item An additional quadratic property has been derived for \( \Psi \) and shown in~\cref{prop:config_error},
    \item The quadratic property of \( \Psi \) requires the derivation of the hessian of \( \Psi \) given in~\cref{proof:config_error},
    \item Additional detail has been included on the set \( D \) and it's properties in~\cref{proof:eR_dot_bound}.
    \item The Lyapunov function in~\cref{proof:adaptive_control} is shown to be positive definite,
    \item The revised stability proof includes a modified requirement for the constant \( c \) shown in~\cref{eqn:c_bound},
\end{itemize}
Here we present the modifications and provide additional detail. 
In addition, we duplicate the modifications from the manuscript in this section as well.

@@

    which is positive definite since \( B > 1\) and \( \sum g_i > g_i\). 
    From~\cite[Proposition 6.30]{bullo2004}, \( \Psi \) is locally quadratic on the set \( D_1 \) which proves~\cref{item:prop_psi_quadratic}.
\end{correction}

The set 
\[ D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} \]
of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists an \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e. the desired attitude should be sufficiently far away from the constraints. 
We can ensure that \( D \) is an open neighborhood of \( R_d \) by choosing \( \epsilon = \min \braces{\psi, \Psi(R|r^T R^T v = \beta,R_d)}\).
Therefore, the given domain \( D \) is an open neighborhood of the desired attitude configuration, \(R_d\), and the Lyapunov stability results are valid in this domain.

The proof of~\Cref{prop:adaptive_control} given in~\Cref{proof:adaptive_control} has been improved to explicitly demonstrate that \( \mathcal{V} \) is positive definite.
\begin{correction}
    Consider the Lyapunov function \( \mathcal{V} \) given by
    \begin{align*}
    \mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , %\label{eqn:v_adapt}
    \end{align*}
    over the domain \( D_3 = D_1 \cap D_2\), which ensures that the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.

@@

Finally, the bounds on \( c \), given in~\cref{eqn:c_bound}, have been modified to ensure that \( W_1, W_2\) and \( M \) are all positive definite.
\begin{correction}
    If \( c \) is chosen such that
    \begin{gather}
        0 < c < \min \braces{\sqrt{\frac{2 k_R n_1}{\lambda_m}},\sqrt{\frac{2 k_R n_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} .
    \end{gather}
    the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is  bounded.
\end{correction}
\item \textit{Typo in eq. (40).}

@@

The bounds on \( c \) have been modified due to the additional detail in the stability proof shown in~\Cref{proof:adaptive_control}.

The equation has been modified as:
\begin{correction}
    \begin{gather}
        0 < c < \min \braces{\sqrt{\frac{2 k_R n_1}{\lambda_m}},\sqrt{\frac{2 k_R n_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} .
    \end{gather}
\end{correction}

### 2017-01-06 Response.tex

The proof of~\Cref{prop:adaptive_control} given in~\Cref{proof:adaptive_control} has been improved. 
Originally, the positive definiteness of \( \mathcal{V}\) was not explicitly defined. 
\Cref{prop:eR_dot_bound} has been modified to include additional detail on the upper bound of \( A(R) \) as:
\begin{correction}
    Upper bounds of \( A(R) \) and \( B(R) \) are given by
    \begin{gather}
        \norm{A} < b_2 \norm{e_{R_A}}^2 = c_A  , \quad \norm{B} < c_B . 
    \end{gather}
  where the constant \( b_2\) is given by \( b_2 = \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi}}\) for
  \begin{align*}
    h_4 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
    h_5 &= \min\braces{\parenth{g_1 + g_2}^2,\parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} .\\
  \end{align*}
\end{correction}

The domain \( D \) is chosen to both exclude the undesired critical points of \( A(R)\) as well as the infeasible regions defined by the constraints. 
In general, this is not a difficult assumption to satisfy as the desired attitude will typically be located far from the constrained regions.
We have augmented the manuscript with some additional discussion of the chosen domain \( D \) in~\Cref{proof:eR_dot_bound}.

\begin{correction}
    We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
    Furthermore, one can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
    The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
    The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
    This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
    Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
\end{correction}

Subsequently,~\Cref{prop:adaptive_control} was modified to explicitly demonstrate that \( \mathcal{V} \) is positive definite.
\begin{correction}
    Consider the Lyapunov function \( \mathcal{V} \) given by
\begin{align*}
    \mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , %\label{eqn:v_adapt}
\end{align*}
over the domain \( D \) in~\cref{eqn:domain}.
From~\Cref{prop:eR_dot_bound,prop:config_error}, the configuration error function is bounded in \( D \) by
\begin{align*}
    b_1 \norm{e_{R_A}}^2 < b_1 \norm{e_{R}}^2 < \Psi < b_2 \norm{e_{R_A}}^2 < b_2 \norm{e_{R}}^2 .
\end{align*}
Using this the Lyapunov function \( \mathcal{V} \) is bounded by
\begin{align*} %\label{eqn:v_upper_bound}
    z^T W_1 z \leq \mathcal{V} \leq z^T W_2 z ,
\end{align*}
where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrices \(W_1,W_2 \in \R^{3 \times 3}\) are given by
\begin{align*}
    W_1 & = \begin{bmatrix}
        k_R b_1 & \frac{1}{2} c \lambda_m & 0 \\
        \frac{1}{2} c \lambda_m & \frac{1}{2} \lambda_m & 0 \\
        0 & 0 & \frac{1}{2 k_\Delta}
    \end{bmatrix},\\
    W_2 & = \begin{bmatrix}
        k_R b_2 & \frac{1}{2} c \lambda_M & 0 \\
        \frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
        0 & 0 & \frac{1}{2 k_\Delta}
    \end{bmatrix} .
\end{align*}
The time derivative of \( \mathcal{V}\) with the control input defined by~\cref{eqn:adaptive_control} is given as
\begin{align}
    \dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
    &- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
\end{align}
where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
\begin{align*}
     e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
\end{align*}
Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
\begin{gather*}
    \dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
\end{gather*}
where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
\begin{gather*}
    M = \begin{bmatrix}
        k_R c & \frac{k_\Omega c}{2} \\
        \frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
    \end{bmatrix} .
\end{gather*}
If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then the matrices \( W_1, W_2 \) and \( M \) are positive definite.
This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D$. As such, the zero equilibrium is stable in the sense of Lyapunov, and all of the error variables are bounded. Furthermore, $\lim_{t\to\infty} \zeta=0$ according to the LaShalle-Yoshizawa theorem~\cite{khalil1996}. 
\end{correction}
